---
title: "Plotting Assignment"
author: "Maikol Monticelli"
date: "2025-02-09"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---

# Loading dependencies
```{r dependencies}
# Loading some packages for plotting
library(readr)
library(ggplot2)
library(scales)
library(dplyr)
library(tidyr)
library(ThemePark)
library(patchwork)
library(janitor)
library(knitr)
library(kableExtra)

```

# Data generation
```{r data generation}

# Setting the random seed
set.seed(123)

# Simulating the data
n <- 100
game_agression <- data.frame(
  x = rnorm(n, mean = 50, sd = 10),
  y = rnorm(n, mean = 100, sd = 20)
)
```

# Plotting

## Bad Plot

### Coding the bad plot 
```{r bad plot}
plot_bad <- ggplot(game_agression, aes(x = x, y = y)) +
# Adding  extreme colors and making the lining worse by dotting it
  geom_point(color = "pink", size = 7, shape = 8) +             
  geom_smooth(method = "lm", se = FALSE, color = "red", linetype = "dotted") +
# The void theme has no axes, ticks or gridlines
  theme_void() +                                                 
  ggtitle("Connection between games and agression")                                     

```

```{r print and save bad plot}
# Printing and saving the bad plot
print(plot_bad)
ggsave("plot_bad.png",plot = plot_bad,bg= "white")

```

### Why is this a bad plot?

 - Only the title but no more information given, it makes the interpretation really difficult.
 - Choosing a theme that is not good for the type of plot, by completely wiping the axes, ticks and gridlines.
 - Really distracting colors and dot type, this makes the data look cluttered and distracting
 - The colors are not color blindness friendly


## Good plot

### Coding the good plot

```{r good plot}
plot_good <- ggplot(game_agression, aes(x = x, y = y)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +    
# Regression line with confidence interval
  geom_smooth(method = "lm", se = TRUE, color = "darkblue") +        
  labs(
# Defining title,x,y and caption   
     title = "The interplay between games and agression",
    x = "Game Time in min",
    y = "Agression Value",
    caption = "The data was simulated thanks to R, n=100"
  ) +
  theme_minimal(base_size = 14) + 
# Centering and making the Title appealing
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.caption = element_text(size = 10, hjust = 1)
  )

```

```{r print and save good plot}
# Printig the good plot
print(plot_good)
ggsave("plot_good.png",plot = plot_good, bg= "white")

```

### Why is this a good plot?

 - Clear description of x and y axes and a detailed title to give the reader all the information needed. 
 - Good coloring and making it okay for everyone, taking the most common color blindness in consideration.
 - Choosing a simple and modern theme to make it more attractive.
 - Slightly transparent points so that the data doesn't seem cluttered and you can see layering dots.
 - Decent scaling values
 - Adding the confidenc interval to make the interpretation easier.


# Grading
In my opinion I did a a decent job therefore deserving a 4,5-5 for the plotting.

 - The bad plot is really messy and unreadable.
 - The good plot is clear and readable.
 
```{r}
sessionInfo()
```
 
