---
title: "Plotting Assignment"
author: "Maikol Monticelli"
date: "2025-02-05"
output:
  html_document:
    code_folding: show
    highlight: haddock
    theme: flatly
    toc: yes
    toc_float: yes
---


```{r}
# Loading some packages for plotting
library(readr)
library(ggplot2)
library(scales)
library(dplyr)
library(tidyr)
library(ThemePark)
library(patchwork)
library(janitor)
library(knitr)
library(kableExtra)

```

```{r}

# Setting the random seed
set.seed(123)

# Simulating the data
n <- 100
game_agression <- data.frame(
  x = rnorm(n, mean = 50, sd = 10),
  y = rnorm(n, mean = 100, sd = 20)
)
```

# Bad Plot
## Why is this a bad plot?:
 - Not matching colors and simbols 
 - Only the title but no more informations given, it makes the interpretation really difficult
 - Chosing a theme that is not good for the type of plot 
 - Zu starke Markierungspunkte (überladen)
 
```{r}
plot_bad <- ggplot(game_agression, aes(x = x, y = y)) +
  geom_point(color = "pink", size = 5, shape = 8) +             
  geom_smooth(method = "lm", se = FALSE, color = "red", linetype = "dotted") +
  # The void theme has no roster or background
  theme_void() +                                                 
  ggtitle("Connection between games and agression")                                     

```

```{r}
# Ausgabe des schlechten Plots
print(plot_bad)

```

# Good plot
## Why is this a good plot?:
 - Klare und aussagekräftige Achsenbeschriftungen und Titel
 - Passende Farbauswahl und angemessene Punktgrößen
 - Chosing a simple and modern theme to make it more attractive

```{r}
plot_good <- ggplot(game_agression, aes(x = x, y = y)) +
  geom_point(color = "steelblue", size = 3, alpha = 0.7) +    
# Regression line with confidence interval
  geom_smooth(method = "lm", se = TRUE, color = "darkblue") +        
  labs(
    title = "The interplay between x and y",
    x = "X-Werte",
    y = "Y-Werte",
    caption = "The interplay between x and y "
  ) +
  theme_minimal(base_size = 14) +                                   
  theme(
    plot.title = element_text(face = "bold", hjust = 0.5),
    plot.caption = element_text(size = 10, hjust = 1)
  )

```


```{r}
# Ausgabe des guten Plots
print(plot_good)

```

